Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-02-27 tex/m2ef/dnpp_referee_response.tex

We list here a detailed list of responses Referee's major remarks. We address the minor remarks directly in the text.

\begin{enumerate}

 \item \textit{[Both in Abtract and Introduction, the presentation of the problem to deal with is not well structured. As a matter of fact, first the TVS is briefly introduces, then options and TVO are only hinted, and lastly the problem is shortly described, without all these topics are well linked each other. I suggest the authors to improve this presentation.]}

 We have conducted a comprehensive review of the crucial components of the abstract and introduction sections to ensure that the reader is presented with a lucid and concise overview of the problem being addressed. In the introduction, our focus was primarily on establishing a stronger connection between TVSs and the derivatives market, which are based on these underlying assets. Furthermore, we have expounded upon and elucidated the description of the problem addressed in this paper, with a particular emphasis on the methods employed and the resultant findings. It is hoped that this will enable the reader to contextualize our work more effectively within the pertinent literature.

@@

 \item \textit{[The Authors address the investigated continuous stochastic control problem through two different approaches: an exact one providing the analytical solution of the problem, and an approximate one based on RL. As for the previous point, even in this one the connections between the two solution approaches are not entirely intelligible. In other terms, it is not entirely clear how the two approaches relate each other. Is the approximate one necessary given that the exact approach provides an analytical solution to the problem? What is the "utility" to use an approximate approach given the applicability of an exact one? I suggest the Authors to clarify this issue.]}

The analytical solution applies only for a specific choice of the model for the dynamics of the underlying and under suitable hypotheses on the payoff. We added equation (52) and a sentence in the first paragraph of section 4 to stress this point. Furthermore, we have enhanced the clarity of this point in the introduction section where we explicate the contribution of this work.

@@

 \item \textit{[In Subsection 3.3, three (so-called intuitive) strategies are introduced, $S_A$, $S_B$ and $S_C$. No rationales are provided concerning their choices. I suggest the Author to give some details about this point.]}

 The three \quotations{intuitive strategies} presented in this paper represent plausible expert-based approaches that a practitioner may choose to adopt when addressing the control problem. We have provided further elucidation on this matter in Subsection 3.3, where we have also incorporated the financial implications of these strategies.

@@

 \item \textit{[In Section 4, the Authors state that ``[t]he first [RL] method is a specific algorithm developed by us to fit the problem [...]''. As know, an important feature of any RL method is its convergence to the (unknown) best policy, if any. The Authors do not spend words about this characteristic of the specific algorithm they developed and applied, so I ask them to give some detail about this topic.]}

 The intention behind the sentence was to apprise the reader that the first algorithm was developed by the authors themselves to tackle the problem at hand. In formal terms, it can be classified as a direct policy search algorithm that relies on gradient-based optimization of the Monte Carlo outcome obtained from numerical simulations. This kind of algorithms is well-known in the Reinforcement Learning literature. We have revised this statement to ensure that its meaning is conveyed with greater clarity.

### 2023-02-27 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
complete dnpp_referee_response + some paper little corrections

\change{In the second part of our work we tackle the problem in the general case of a state-dependent dynamics for the risky assets for which only the numerical approach is admissible.}
\remove{Although from a theoretical point of view this solution represents a sub-optimal strategy when dealing with generic dynamics for the risky assets, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem}. More precisely we numerically study the problem \remove{in the general case of  a local volatility dynamics \cite{Derman1994}, \cite{Dupire1994} by adopting a Reinforcement Learning approach, in particular an \textit{ad hoc} vanilla direct policy algorithm and the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}} \change{assuming a local volatility (LV) dynamics \cite{Derman1994}, \cite{Dupire1994} \change{for the risky assets}. The reason for selecting the LV model is its widespread adoption in the industry to value derivatives, especially those related to asset baskets \cite{Gatheral2006}. The LV investigation is based on a Reinforcement Learning approach, in particular through an \textit{ad hoc} direct policy search algorithm and the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}. From our study, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem under the LV dynamics.}
\\

@@

In our work we adopt two learning strategies to compare their performances in terms of overall reward: an \textit{ad hoc} direct policy \change{search} algorithm and the state of the art proximal policy optimization (PPO) developed in \cite{Schulman2017} and \cite{Schulman2016}.

The first method is a specific algorithm developed by us to fit the problem aim to find the optimal option price; this technique can take place as a direct policy optimization method in the wide taxonomy of Reinforcement Learning algorithms. We will go into details in Section~\ref{sec:direct_policy}.

>>>>

\change{In the second part of our work we tackle the problem in the general case of a state-dependent dynamics for the risky assets for which only the numerical approach is admissible.}
\remove{Although from a theoretical point of view this solution represents a sub-optimal strategy when dealing with generic dynamics for the risky assets, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem}. More precisely we numerically study the problem \remove{in the general case of  a local volatility dynamics \cite{Derman1994}, \cite{Dupire1994} by adopting a Reinforcement Learning approach, in particular an \textit{ad hoc} vanilla direct policy algorithm and the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}} \change{assuming a local volatility (LV) dynamics \cite{Derman1994}, \cite{Dupire1994} \change{for the risky assets}. The reason for selecting the LV model is its widespread adoption in the industry to value derivatives, especially those related to asset baskets \cite{Gatheral2006}. The LV investigation is based on a Reinforcement Learning approach due to the high-dimensionality problema we deal with. In particular we compare the performances of a plain direct policy search gradient-based algorithm with those of the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}. At the end of our study, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem under the LV dynamics.}
\\

@@

In our work we adopt two learning strategies to compare their performances in terms of overall reward: \remove{an \textit{ad hoc}} \change{a plain} direct policy \change{search} algorithm and the state of the art proximal policy optimization (PPO) developed in \cite{Schulman2017} and \cite{Schulman2016}.

The first method is \change{well-known in RL literature \cite{Sutton2018}: it is based on the direct update of the agent policy via a gradient-based optimization of the value function.}\remove{a specific algorithm developed by us to fit the problem aim to find the optimal option price; this technique can take place as a direct policy optimization method in the wide taxonomy of Reinforcement Learning algorithms}. We will go into details in Section~\ref{sec:direct_policy}.
